---
title: "Data 607 Week 4 Homework"
author: "Armenoush Aslanian-Persico"
output:
  html_document:
    highlight: tango
    theme: cerulean
  pdf_document: default
---

---
### Automated Data Collection in R, Chapter 8, Problems 3, 7, 8, 9.

### Load Packages
```{r}
library(stringr)
library(XML)
library(RCurl)
```

### #3
#### Print names in the correct order: Title, First, Last.
Split names by comma, flip, combine.
```{r}
name<- c(
  "Moe Szyslak",
  "Burns, C. Montgomery",
  "Rev. Timothy Lovejoy",
  "Ned Flanders",
  "Simpson, Homer",
  "Dr. Julius Hibbert")

hascomma<-str_detect(name,",")
hascomma

splitname<-str_split(name,",")
splitname

flipname<-sapply(splitname,rev)
flipname

goodname<-str_c(flipname,sep=" ")
goodname
# Needs work.
```

#### Determine if the name has a title. 
Look for 2 or more letters followed by a period.
```{r}
hastitle<-str_detect(name,"[[:alpha:]]{2,}\\.")
hastitle
```

#### Determine if the name has two first names.
Look for 1 uppercase letter followed by a period.
```{r}
multiplenames<-str_detect(name,"[[:upper:]]{1}\\.")
multiplenames
# This would not detect first names without a period.
```

### #7
#### Extract first html tag only.
The original expression failed because it was extracting the longest matching result. To get the desired result, we can extract the tag with only letter (alpha) characters.
```{r}
astring<-c("<title>++BREAKING NEWS+++</title>")
firsttag<-str_extract(astring,"<[[:alpha:]]+>")
firsttag
```

### #8
#### Extract binomial formula.
The original expression failed because it did not capture the carat or minus sign.
```{r}
bstring<-c("(5-3)^2=5^2-2*5*3+3^2 conforms to the binomial theorem")
bformula<-str_extract(bstring,"[0-9=+*()+\\^\\-]+")
bformula
```

### #9
#### Extract secret message.
```{r}
secretmessage <- c("clcopCow1zmstc0d87wnkig7OvdicpNuggvhryn92Gjuwczi8hqrfpRxs5Aj5dwpn0TanwoUwisdij7Lj8kpf03AT5Idr3coc0bt7yczjatOaootj55t3Nj3ne6c4Sfek.r1w1YwwojigOd6vrfUrbz2.2bkAnbhzgv4R9i05zEcrop.wAgnb.SqoU65fPa1otfb7wEm24k6t3sR9zqe5fy89n6Nd5t9kc4fE905gmc4Rgxo5nhDk!gr")
decode<-unlist(str_extract_all(secretmessage,"[[:upper:]]|\\."))
combined<-str_c(decode,sep="",collapse ="")
answer<-gsub("\\."," ",combined)
cat(answer)
justforme<-(str_c(answer, " ARMENOUSH"))
cat(justforme)
```
